A Data-Driven Framework for Neural Field Modelling

### 2010-10-29 ltx/first_order_framework/SupportingInformation.tex
commiting for merge

The stimulation for the current source consisted of a 40~Hz sine wave with a duration of 1~s. The recording from the central electrode was used construct the sensor kernel. To extract the amplitude the signal the data was first band-pass filtered with a centre frequency of 40~Hz. The the envelope of the signal was found by
\begin{equation}
	a = \frac{1}{N}\sum_n{\sqrt{(x(n)-\mathcal{H}x(n))^2}}
\end{equation}
where
\begin{figure}[h]
	\begin{center}
	\includegraphics[scale=1]{./Graph/eps/channel3fig.eps}
	\end{center}
	\caption{Amplitude of the envelope of the signal recorded from an electrode at the origin as the source was moved.}
	\label{fig:Ch3}
\end{figure}

>>>>

The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s. The recording from the central electrode was used construct the sensor kernel. To extract the amplitude the signal the data was first band-pass filtered with a centre frequency of 40~Hz. The envelope of the signal was found by computing the mean instantaneous amplitude computed by
\begin{equation}
	a = \frac{1}{N}\sum_n{\sqrt{(x(n)-\mathcal{H}x(n))^2}}
\end{equation}
where $\mathcal{H}$ denotes the Hilbert transform operator, $n$ indexes samples and $N$ is the total number of samples in the time series.

\begin{figure}[h]
	\begin{center}
	\includegraphics[scale=1]{./Graph/eps/channel3fig.eps}
	\end{center}
	\caption{Amplitude of the envelope of the signal recorded from an electrode at the origin as the source was moved.}
	\label{fig:Ch3}
\end{figure}
